%%
%% ASSETS Poster Extended Abstract
%% StrengthFlow: Task Management for ADHD via Cognitive Strengths
%%
\documentclass[sigconf]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
  Bib\TeX}}}

\setcopyright{acmlicensed}
\copyrightyear{2025}
\acmYear{2025}
\acmDOI{XXXXXXX.XXXXXXX}
\acmConference[ASSETS '25]{The 27th International ACM SIGACCESS Conference on
  Computers and Accessibility}{October 26--29, 2025}{Denver, CO, USA}
\acmISBN{978-1-4503-XXXX-X/2025/10}

\begin{document}

\title[StrengthFlow: ADHD Task Management via Cognitive Strengths]{StrengthFlow: A Strength-Based Task Management Application for Adults with ADHD}

\author{Jingyu Lei}
\affiliation{%
  \institution{University of Cambridge}
  \department{Department of Architecture}
  \city{Cambridge}
  \country{United Kingdom}}
\email{jl2557@ca.ac.uk}

\author{Lan Xiao}
\affiliation{%
  \institution{University College London}
  \department{Department of Computer Science, DDI}
  \city{London}
  \country{United Kingdom}}
\email{l.xiao.22@ucl.ac.uk}

\renewcommand{\shortauthors}{Lei}

\begin{abstract}
ADHD is commonly framed through hyperactivity, impulsivity, inattention, and executive-function difficulties, while its associated cognitive strengths receive less attention. Existing task management applications often rely on reminders, timers, and behavioural correction, potentially reinforcing deficit-orientated assumptions.

This paper presents StrengthFlow, a strength-based task management application for adults with ADHD. It translates six ADHD-related cognitive strengths into design principles addressing challenges in activation, concentration, effort, emotion, memory, and task execution. A high-fidelity prototype was preliminarily evaluated with three adults with ADHD. Feedback indicated positive responses to its strength-based framing and visual design, while highlighting the need to better support use in distracting environments. StrengthFlow demonstrates how neurodiversity-informed design can promote capability, autonomy, and positive identity, reflecting the principle that “people with differences may not need a cure; they need help and accommodation.”

\end{abstract}

\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10003120.10003121</concept_id>
  <concept_desc>Human-centered computing~Human computer interaction (HCI)</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10003120.10003121.10003124</concept_id>
  <concept_desc>Human-centered computing~Interactive systems and tools</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10003120.10003121.10003125.10010595</concept_id>
  <concept_desc>Human-centered computing~User interface programming</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Human computer interaction (HCI)}
\ccsdesc[300]{Human-centered computing~Interactive systems and tools}
\ccsdesc[100]{Human-centered computing~User interface programming}

\keywords{ADHD, Neurodiversity, Cognitive advantages, Digital application,
  Assistive technology, Task management}

\maketitle

\section{Introduction}

Behavioural characteristics of ADHD do not exist in a binary form of normal and
abnormal~\cite{sedgwick2019}. A person with ADHD experiences deficits in
cognitive control, sensitivity to rewards, and time perception, while
simultaneously displaying high energy, creativity, hyperfocus, empathy, and
willingness to help others. The core deficit is \textbf{executive dysfunction}
\cite{nigg2005}---a broad range of top-down cognitive processes and abilities
that enable flexible, goal-directed behaviour~\cite{miyake2000}---which
significantly affects the daily social activities of adults with ADHD.

Current approaches to alleviating executive symptoms include traditional
medications---whose global market continues to grow~\cite{scheffler2007}---and
behavioural therapies; however, they cannot maintain long-term symptom relief
and have severe limitations in terms of side effects~\cite{enriquez2019},
making psychosocial interventions a necessary complement~\cite{safren2006}. One widely adapted psychosocial tool is the
digital application. A systematic review of 355 app-related studies found that
most effectiveness outcomes were negative~\cite{pasarelu2020}: poor outcomes
were not maintained long after the intervention~\cite{gajecki2014}, and users
reported more severe anxiety when separated from the tool~\cite{torous2016}.
More critically, these control-oriented tools reinforce the negative mental
model that ``I need to be managed,'' undermining self-esteem.

Brown's model of ADHD executive functioning identifies six impairment
dimensions---activation, concentration, effort, emotion, memory, and
execution. A complementary qualitative study defines six positive core themes in
ADHD: \textbf{cognitive vitality}, \textbf{courage}, \textbf{energy},
\textbf{humanity}, \textbf{resilience}, and \textbf{transcendence}
\cite{schippers2022}. StrengthFlow maps each cognitive strength to its
corresponding executive challenge and implements an interaction module that
activates the strength to support task engagement.

\section{Related Works}

The neurodiversity of executive functions in ADHD is concentrated in four brain
regions: the prefrontal cortex, the basal ganglia, the cerebellum, and the
parietal-temporal region, operating through the reticular activating
system~\cite{castellanos2002,valera2007,nakao2011,durston2004}. These regions
cannot be categorised independently; they form a dynamic, integrated management
process in which executive processing depends on coordinated activity across
multiple cognitive components. This section analyses that neurodiversity by (i)~examining the
neural connections through which positive and negative characteristics can be
interchanged, (ii)~reviewing functional modules of existing ADHD management
applications, and (iii)~reviewing the interaction design principles required for
mobile application development. All three inform the StrengthFlow prototype.

\subsection{Research Overview}

A fundamental assumption of the neurodiversity paradigm is that all forms of
neurological variation are valuable~\cite{denhouting2019}. Within this paradigm,
qualitative research by Sedgwick et al.~\cite{sedgwick2019} and Schippers
et al.~\cite{schippers2022} identifies six core positive themes in adults with
ADHD: \textbf{cognitive vitality}, \textbf{courage}, \textbf{energy},
\textbf{humanity}, \textbf{resilience}, and \textbf{transcendence}. Brown's
executive functioning model~\cite{nigg2005} identifies six corresponding
impairment dimensions: \textbf{activation}, \textbf{concentration}, \textbf{effort}, \textbf{emotion}, \textbf{memory}, and
\textbf{execution}. The six dimensions within this model map one-to-one
onto the six positive themes, a structural correspondence arising from shared
neural substrates: the same brain regions and networks that produce each
executive impairment also generate the corresponding cognitive
strength~\cite{castellanos2002,valera2007,nakao2011,durston2004}. Each
strength is therefore a principled, neurologically grounded compensatory advantage for its paired deficit. The six pairings and their neural bases are as follows.

\textbf{Cognitive Vitality vs.\ Concentration.}
Cognitive vitality is the first positive core theme of ADHD and corresponds to
the executive impairment of concentration. Its conceptualisation summarises the
uninterrupted mental activity of people with ADHD, spontaneous and
non-sequential thought processes, flashes of images, and intense mental
concentration---defined as a perception of an intensely pleasurable
self-experience as an effective agent of change that, through its intervention,
can rapidly alter the course of events~\cite{stine2008,ammaniti2013}. The
corresponding neural system is the brain's default mode network (DMN), which is
negatively activated during external attention tasks and positively activated
during internal psychological tasks related to the self, moral judgements,
situational memories, and future visions~\cite{sestieri2011}. In ADHD the DMN
remains persistently active, producing the inability to focus on and complete
external tasks for long periods; neurodiversity is thus reflected in the
inability to concentrate on external tasks and the inability to disengage when
an internal task demands continuation.
\textbf{Design implication:} The cognitive dynamism of divergent thinking,
creativity, curiosity, and a quick knowledge base may be used as a management
tool~\cite{mole2022} for redirecting attention towards externally required
tasks.

\textbf{Courage vs.\ Emotion.}
Courage is the second positive core theme and corresponds to the executive
impairment of emotion. Its conceptualisation summarises the process by which
people with ADHD face their fears and deal with uncertainty---defined as the
struggle to overcome the need for recognition and strive for individualisation:
a struggle to transcend restrictive social norms and beliefs through resistance
to cultural adaptation or self-determination~\cite{williams2008}. The neural
system implicated is the amygdala, richly interconnected with the thalamus and
ventral striatum, playing a crucial role in emotion regulation and reward
representation. In ADHD the amygdala is over-activated, including in surface
morphology and dopamine receptor density~\cite{plessen2006}, while the ventral
striatum is under-activated~\cite{plichta2014}. Executive dysfunction manifests
as restlessness, inadequate emotional self-regulation, and impulsivity.
Neurodiversity is reflected in low responsiveness to positive stimuli and
over-perception of negative stimuli~\cite{du2006}; rapid decision-making is
possible in the face of short-term rewards, but aversive delays occur in the
anticipation and acceptance of long-term rewards~\cite{knutson2001}.
\textbf{Design implication:} Non-conformity, risk-taking, integrity, and
persistence in courage may be used as management tools to reduce procrastination,
though not to prevent emotional outbursts.

\textbf{Energy vs.\ Activation.}
Energy is the third positive core theme and corresponds to the executive
impairment of activation. Its conceptualisation summarises the psycho-energetic
processes that generate positive internal drives in people with ADHD---defined
as willpower motivated by a strong desire to achieve something meaningful,
associated with a sense of purpose, meaning in life, and a collective quest for
higher aspects that encompass the self~\cite{schippers2022}. The neural system
implicated is the dorsal attention network (DAN)~\cite{corbetta2002}, which
functions as the brain's attentional aperture, responsible for focusing and
directing attention to salient stimuli. In ADHD the DAN is more active than the
ventral attention network (VAN), resulting in a higher selective top-down
allocation of attention than adaptive bottom-up attention~\cite{corbetta2002}.
The corresponding executive impairment is the inability to activate temporal
task priority: ADHD does not perceive time as a sequence but as a dispersed
collection of events linked to people, activities, and emotions, manifesting as
the inability to organise and prioritise tasks. Yet people with ADHD become
hyperfocused when an ambitious personal goal is present~\cite{schippers2022}.
\textbf{Design implication:} Willpower to achieve meaningful goals may be used
as a management tool to activate prioritised tasks and reorder the ADHD chaotic
concept of time.

\textbf{Humanity vs.\ Execution.}
Humanity is the fourth positive core theme and corresponds to the executive
impairment of execution. Its conceptualisation summarises the social
identification processes of social intelligence~\cite{humphrey1976}, humour,
self-acceptance, and feelings when engaging in social behaviour---positioned as
establishing management relationships through higher emotional
intelligence~\cite{salovey1990}, empathy, awareness, and attitude. The neural
system implicated is the mirror neuron system, which produces the same internal
feelings in the observer as in the person observed expressing an emotion. The
corresponding executive impairment is difficulty in changing one's behaviour:
neurodiversity is reflected in the tendency to emit positive energy and affect
others during complex social events, while simultaneously being unable to adapt
behaviour when others are puzzled or upset.
\textbf{Design implication:} Positive energy in human nature may be used as an
extension tool to maintain positive emotions in people with ADHD, though
behaviour change requires additional tools to intervene.

\textbf{Resilience vs.\ Effort.}
Resilience is the fifth positive core theme and corresponds to the executive
impairment of effort. Its conceptualisation describes the process of
self-regulation and self-protection under adverse conditions, including
behavioural adjustment strategies for self-adherence~\cite{garmezy1971}. The
neural system implicated is the anterior cingulate cortex, located in the medial
frontal lobe, which plays an extensive role in cognitive control and behavioural
monitoring~\cite{carter2007}. The corresponding executive impairment is the
inability to manage alertness: when antagonistic conflict arises, people with
ADHD exercise a degree of self-control but then experience ineffective
self-regulation due to mental fatigue caused by ego
depletion~\cite{baumeister2000}.
\textbf{Design implication:} Self-regulation strategies in resilience may not
function as a stand-alone management tool; they should be combined with other
adjustment strategies and offered as flexible, optional choices.

\textbf{Transcendence vs.\ Memory.}
Transcendence is the sixth and final positive core theme and corresponds to the
executive impairment of memory. Its conceptualisation describes the sensory
process of appreciating beauty and excellence in people with ADHD, typically in
the case of music. Appreciation of beauty and excellence is a topic in positive
psychology~\cite{martinez2016}, defined here as the feeling of being rapidly
astonished by talent in the environment, with associated feelings of awe,
wonder, and deep memorisation~\cite{shiota2006}. The neural system implicated is
the corticocerebellar network with norepinephrine, which generates the internal
links responsible for working memory. In ADHD, these norepinephrine links are
less activated; neurodiversity is reflected in the fact that people with ADHD
show high absorption and openness to experience when recalling events related to
artistic beauty, yet are unable to recall stimulus- and stress-free details.
\textbf{Design implication:} Deep memorisation through appreciation of artistic
beauty in transcendence may be used as a component tool to support and deepen
working memory.

\subsection{Mobile Tools Research}

\subsubsection{User Interaction Design.}
Mental models---abstract cognitive structures through which users interpret and
predict an application~\cite{rook1993}---are the key to user-centred
design~\cite{ruiz2021}. Visual, symbolic, and pictorial design elements are the
primary medium through which mental models are conceptualised~\cite{goldschmidt2007,ourusoff1985},
and knowledge management frameworks suggest that structuring information around
action-relevant schemas supports effective retrieval and
application~\cite{ruggles1998}. From a systematic review of 257 widely cited UI
design principles, six core guidelines were identified: providing informative
feedback, minimising memory load, clear error messages, providing shortcuts,
using natural language, and using real-world metaphors~\cite{ruiz2021}. The
inherent mental model of people with ADHD is largely negative (``I need to be
managed''); StrengthFlow's framework must extend this model with positive
elements through a virtuous-circle design logic.

\subsubsection{Interactive Modules.}
A review of 22 representative ADHD management applications (10,000--50,000
downloads) was conducted, covering diagnostic tools, task management, habit
building, time management, focus enhancement, emotion regulation, memory
support, and financial management~\cite{pasarelu2020}. Table~\ref{tab:apps}
summarises the resulting module analysis by dysfunction. The review reveals that
most modules address symptoms through mandatory reminders and timers with no
leverage of ADHD cognitive strengths, while a subset---mapping, meditation,
community interaction, and random creative prompts---do align with positive ADHD
characteristics. No existing tool integrates these strength-aligned modules into
a unified framework.

\begin{table*}
  \caption{ADHD application module analysis: dysfunction targeted, interaction
    type, and whether the module leverages ADHD cognitive strengths (adapted
    from review of 22 representative apps).}
  \label{tab:apps}
  \begin{tabular}{p{0.10\linewidth} p{0.16\linewidth} p{0.20\linewidth}
                  p{0.30\linewidth} c}
    \toprule
    \textbf{Dysfunction} & \textbf{Symptom} & \textbf{Module} &
    \textbf{Interaction Element} & \textbf{Leverages Strengths?} \\
    \midrule
    Activation  & Time chaos            & Task reminder    & Mandatory reminder          & No  \\
    Activation  & Time chaos            & Label / tagging  & Information capture          & Yes \\
    Focus       & Lack of attention     & Timer            & Mandatory countdown          & No  \\
    Effort      & Inability to sustain  & Timer            & Mandatory countdown          & No  \\
    Emotion     & Impulsive decision    & Meditation       & Mindful relaxation           & Yes \\
    Memory      & Missing tasks         & Mapping          & Visual spatialisation        & Yes \\
    Execution   & Cannot adjust behaviour & Habit tracker  & Self-awareness, personalised time & Yes \\
    Social      & Low positive mood     & Community        & Patient interaction          & Yes \\
    Creativity  & Dispersed thinking    & Random prompts   & Idea generation              & Yes \\
    \bottomrule
  \end{tabular}
\end{table*}

\subsection{Research Conclusions}

Across 22 reviewed applications, existing ADHD task-management tools rely
primarily on mandatory reminders, countdown timers, and behavioural correction,
with only isolated modules---visual mapping, meditation, and random creative
prompts---aligned with positive ADHD characteristics~\cite{pasarelu2020}. None
of the identified applications integrates strength-aligned elements within a
coherent, theoretically grounded framework; each tool remains anchored in a
deficit-correction posture that reinforces the negative mental model that the
user is a problem to be managed. This gap motivates the strength-based design
framework presented in Section~3, which translates the six cognitive
strength--executive challenge pairings into abstract design principles as the
conceptual foundation for StrengthFlow.

\section{User Group and Requirements}

Approximately 2.8\% of adults worldwide have ADHD~\cite{faraone2006}. An
analysis of two qualitative studies (422 adults with ADHD across six countries)
showed that participants described their own strengths---problem-solving, fantasy,
novelty-seeking, deep focus, empathy, resilience---yet received little external
recognition of them. A review of 127 ADHD studies found that 29\% of treated and
56\% of untreated adults reported low self-esteem, and 38--73\% felt their social
functioning was affected~\cite{harpin2016}.

StrengthFlow therefore targets two parallel needs: (1)~social recognition and
affirmation of ADHD strengths; and (2)~support for executive skill and
self-esteem through positive engagement rather than coercion.

\section{Design}

StrengthFlow translates each of the six cognitive strength--executive challenge
pairings identified in Section~2 into a concrete interaction module. Table~\ref{tab:framework}
presents the framework as a whole, mapping each pairing to its associated neural
basis and derived design principle. The subsections below describe the resulting
modules in detail.

\begin{table*}
  \caption{Strength-based design framework: cognitive strengths, executive
    challenges, associated neural basis, and derived design principles.}
  \label{tab:framework}
  \begin{tabular}{p{0.10\linewidth} p{0.12\linewidth} p{0.22\linewidth} p{0.44\linewidth}}
    \toprule
    \textbf{Cognitive Strength} & \textbf{Executive Challenge} &
    \textbf{Associated Neural Basis} & \textbf{Derived Design Principle} \\
    \midrule
    Cognitive Vitality &
      Concentration &
      Default Mode Network (associated with internal ideation; may remain
        persistently active in ADHD during external tasks) &
      Divergent thinking may serve as an entry point for redirecting attention
        toward externally required tasks. \\
    \addlinespace
    Courage &
      Emotion &
      Amygdala and Ventral Striatum (associated with emotional regulation and
        sensitivity to reward timing) &
      Task engagement may be supported by positively framed, short-horizon
        actions that replace aversive or distant outcomes. \\
    \addlinespace
    Energy &
      Activation &
      Dorsal Attention Network (associated with top-down goal-directed
        attention; may produce hyper-focus under personally meaningful goals) &
      Connecting tasks to personally meaningful goals and higher-order purposes
        may support willpower and task initiation. \\
    \addlinespace
    Humanity &
      Execution &
      Mirror Neuron System (associated with empathic resonance and social
        affect) &
      Social connectedness and positive emotional expression may support
        sustained engagement and positive affect during task execution. \\
    \addlinespace
    Resilience &
      Effort &
      Anterior Cingulate Cortex (associated with cognitive control;
        self-regulation may be limited by ego depletion under conflict) &
      Adaptive self-regulation strategies should be offered as flexible and
        optional resources to support coping during cognitive fatigue. \\
    \addlinespace
    Transcendence &
      Memory &
      Corticocerebellar Network with Norepinephrine (associated with working
        memory; aesthetic absorption may facilitate deep encoding) &
      Visually or aesthetically meaningful representations of task-related
        information may support encoding and retention. \\
    \bottomrule
  \end{tabular}
\end{table*}

\subsection{Module Logic}

StrengthFlow implements one interaction module per pairing. Each description
below follows the structure: \textbf{executive challenge / cognitive strength /
derived design principle / StrengthFlow implementation / intended interaction
outcome}.

\textbf{Concentration module (Cognitive Vitality / Concentration).}
\textbf{Executive challenge:} Difficulty sustaining attention on external tasks
due to persistent internal ideation.
\textbf{Cognitive strength:} Spontaneous, non-sequential divergent thinking.
\textbf{Derived design principle:} Use divergent thinking as an entry point for
redirecting attention toward externally required tasks.
\textbf{StrengthFlow implementation:} Users are presented with a set of randomly generated
visual or verbal prompts and asked to produce a creative response that connects
those prompts to the task they need to complete.
\textbf{Intended interaction outcome:} Creative engagement acts as a bridge
between intrinsic ideation and the required extrinsic task, redirecting rather
than suppressing internal cognitive energy.

\textbf{Memory module (Transcendence / Memory).}
\textbf{Executive challenge:} Difficulty retaining task-relevant information in
working memory.
\textbf{Cognitive strength:} Deep aesthetic absorption that may facilitate
encoding during experiences of wonder or beauty.
\textbf{Derived design principle:} Use visually or aesthetically meaningful
representations of task-related information to support encoding and retention.
\textbf{StrengthFlow implementation:} Users enter key task information before an
aesthetically rich interactive activity; each item is embedded within a visually
engaging display and remains retrievable on demand throughout the activity.
\textbf{Intended interaction outcome:} Aesthetic engagement during task entry
and recall supports retention without reliance on rote memorisation or external
reminders.

\textbf{Persistent tasks module (Humanity / Execution).}
\textbf{Executive challenge:} Difficulty maintaining habitual task routines and
adapting behaviour over time.
\textbf{Cognitive strength:} Social empathy, positive emotional contagion, and
social identity.
\textbf{Derived design principle:} Use social connectedness and positive
emotional expression to support sustained engagement during routine task
execution.
\textbf{StrengthFlow implementation:} Ongoing habits and responsibilities are represented
as planets in a personal solar-system visualisation; completing each
responsibility illuminates the corresponding planet, building a positive
social-identity narrative.
\textbf{Intended interaction outcome:} The social-identity metaphor sustains
motivation for habit maintenance without coercive reminders.

\textbf{Long-term tasks module (Courage / Emotion).}
\textbf{Executive challenge:} Aversive responses to long-term reward
anticipation, producing emotional impulsivity and procrastination.
\textbf{Cognitive strength:} Responsiveness to immediate positive stimuli and
risk-taking under short-horizon conditions.
\textbf{Derived design principle:} Support task engagement through positively
framed, short-horizon actions that replace aversive or distant outcomes.
\textbf{StrengthFlow implementation:} Long-term tasks are decomposed into short-term
sub-tasks, each associated with an immediate positive reward upon completion.
\textbf{Intended interaction outcome:} Short-horizon reward cycles reduce
procrastination by replacing aversive delay with achievable, immediate goals.

\textbf{Priority tasks module (Energy / Activation).}
\textbf{Executive challenge:} Difficulty initiating and prioritising tasks that
lack personal significance or a meaningful activation stimulus.
\textbf{Cognitive strength:} Willpower motivated by a strong desire to achieve
something personally meaningful; hyper-focus in the presence of an ambitious
personal goal.
\textbf{Derived design principle:} Connect tasks to personally meaningful goals
and higher-order purposes to support willpower and task initiation.
\textbf{StrengthFlow implementation:} Users adopt a chosen role or persona associated with
a self-determined narrative and complete priority tasks within that imaginative
context, anchoring task execution in personal meaning.
\textbf{Intended interaction outcome:} Embedding the priority task within a
personally meaningful narrative activates goal-directed energy without relying
on external authority or abstract priority ordering.

\textbf{Emotion module (Resilience / Effort).}
\textbf{Executive challenge:} Difficulty sustaining self-regulation over time;
mental fatigue under cognitive load.
\textbf{Cognitive strength:} Capacity for self-regulation and behavioural
adjustment under adverse conditions.
\textbf{Derived design principle:} Offer adaptive coping strategies as flexible
and optional resources during periods of cognitive fatigue.
\textbf{StrengthFlow implementation:} When in a positive affective state, users are
offered social-expression options; when in a negative state, a set of
positive-thinking and guided-reflection resources is available.
\textbf{Intended interaction outcome:} Mood-contingent branching supports coping
without imposing a fixed sequence, preserving user agency during periods of ego
depletion.

\subsection{Workflow}

The application workflow follows a non-linear model: users enter whichever
module matches their current cognitive state rather than following a prescribed
sequence. This respects the temporal experience of ADHD, in which time is
perceived as a dispersed collection of events linked to people and emotions
rather than a sequential schedule.

\subsection{Visual Design Principles}

People with ADHD have heightened visuospatial processing sensitivity. The
StrengthFlow interface therefore uses: non-repetitive, non-patterned layouts;
vivid colours
associated with high energy and positivity; irregular icon shapes that echo
creativity and divergent thinking; and aesthetically distinctive artwork within
task modules. The UI adheres to six empirically validated core principles:
informative feedback, minimal memory load, clear error messages, shortcuts,
natural language, and real-world metaphors~\cite{ruiz2021}.

\section{Prototype}

A high-fidelity prototype was developed from a wireframe framework that
implements the module logic described above. The visual system consistently
applies the design principles across all modules, ensuring that aesthetic
stimulation supports---rather than distracts from---each cognitive strength
activation. The prototype is interactive and supports the full task-entry-to-
completion flow for each module.

\section{User Testing}

Preliminary evaluation was conducted with three anonymous adults with ADHD.
Positive feedback: the application is engaging and the colour palette
successfully attracts and holds attention. Critical finding: in noisy external
environments (e.g.\ commuting), ambient auditory distractions competed with the
visual engagement. As a result, the next iteration of StrengthFlow will integrate background
music and sound effects. Prior research shows that neurofeedback audio
protocols are a well-established adjunctive treatment for ADHD~\cite{enriquez2019},
providing a principled basis for this extension.

\section{Conclusion}

StrengthFlow is, to our knowledge, the first mobile task-management application
grounded in a strength-based neurodiversity framework for ADHD. Rather than
relying on reminders, timers, or behavioural correction, StrengthFlow positions
each cognitive strength as a conceptual basis for an interaction module that
addresses the corresponding executive challenge. The underlying design approach is replicable:
identify a cognitive strength and its associated executive challenge in the
literature, derive an abstract design principle from that pairing, and implement
a concrete interaction that instantiates the principle without imposing
deficit-oriented constraints.

Limitations include a small user testing sample (N\,=\,3) and limited coverage of
users with deafblindness. Future work will expand evaluation and incorporate
neurofeedback technology as wireless EEG device costs continue to fall. Beyond task management, StrengthFlow aims to shift the mental model of ADHD
from ``I need to be managed'' to one that affirms capability and positive
identity.

\begin{acks}
The author thanks the three anonymous ADHD participants who provided user testing
feedback. This work was conducted under UCL ethical guidelines; participants
submitted informed consent via the UCL REDCap platform.
\end{acks}

\section*{Ethics and Privacy Statement}

User testing involved three anonymous adults with ADHD. No personally
identifiable information was collected. Participants provided informed consent
through the UCL REDCap platform in accordance with UCL ethical review guidelines.
The study presents minimal societal risk; the design aims to benefit ADHD users
by affirming their strengths rather than pathologising their differences.

\bibliographystyle{ACM-Reference-Format}
\bibliography{adhd-poster}

\end{document}
\endinput
